---
title: "D5S1"
author: "NM"
format: html
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| message: false

# load libraries ----
library(tidyverse)
```

```{r}
#| include: false
head(starwars, n = 16)
tail(starwars)
dim(starwars)
```

- create a gg plot, scatter, of mass (y) and height (x)
- update the colour of the point so that it changes based on value of 'mass'

```{r}
ggplot(starwars, aes(x = height, y = mass, colour = mass)) +
  geom_point() +
  labs(x = "Height (cm)",
       y = "Mass (cm)")
```

- create a histogram of character heights
- update the fill color to purple and the outside border line of each histogram bin to orange
- update the axis lables
- update your code chunk option so that only your code and output graph appear in the rendered doc (no warning s or messages)

```{r}
#| fig-cap: "This is my figure caption"
#| fig-alt: "This is some alt text"
ggplot(data = starwars, aes(x = height))+
  geom_histogram(fill = "purple", color = "orange")+
  labs(x = "Height (cm)",
       y = "Count (ones)")

```

df$colname

```{r}
starwars$height
sw_height_mean <- round(mean(starwars$height, na.rm = TRUE),3)
```

The mean height of all starwars character is `r sw_height_mean`
